%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Master's Thesis Researcher}
    {STARPORT Organization - LISA Space Mission Consortium}
    {Porto, Portugal}
    {Sep. 2025 - Present}
    {
      \begin{cvitems}
        \item {Developing a prototype ground control dashboard for the European Space Agency's LISA mission to track and visualize multidimensional mission data.}
        \item {Adhering strictly to European Cooperation for Space Standardisation (ECSS) coding standards to ensure software reliability and maintainability.}
      \end{cvitems}
    }
  \cventrytwopositions
    {Teaching Assistant}
    {Faculty of Engineering of the University of Porto} % Organization
    {Porto, Portugal} % Location
    {Mar. 2025 - Jun. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted students in the development of low level C software for interaction with hardware components namely the computers mouse, keyboard, graphics card, RTC, timers and serial port.}
        \item {Technologies: C, Git, Linux, Minix}
      \end{cvitems}
    }
    {Teaching Assistant} % Job title
    {Mar. 2026 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extended the teaching assistant role for Computer Laboratory to the 2025/26 academic year, providing the same support and guidance to students as in the previous year along with the development of new course materials.}
      \end{cvitems}
    }
  \cventrytwopositions
    {Autonomous Systems Department Member} 
    {Formula Student FEUP}
    {Porto, Portugal}
    {Sep. 2023 - Aug. 2024} 
    {
      \begin{cvitems}
        \item {Responsible for the vehicle's state estimation and its integration with the perception and control sub-systems.} 
      \end{cvitems}
    } 
    {Lead of Embedded Software Sub-system} 
    {Sep. 2024 - Sep. 2025} 
    {
      \begin{cvitems}
        \item {Collaborated with hardware engineers to ensure seamless integration of software and hardware components within the racing vehicle system.} 
        \item {Architected and developed the embedded software of the vehicle that competed in international competitions, including the Formula Student Germany 2025. In these events not only the product but also the software development process and the software architecture and design were evaluated.} 
        \item {Technologies used: C, C++, CAN, SPI, ROS2, Git, Linux, ARM, Python, Docker}
      \end{cvitems}
    }

  \cventrytwopositions
    {Research Intern}
    {INESC TEC}
    {Porto, Portugal}
    {Jun. 2023 - Jul. 2023}
    {
      \begin{cvitems}
        \item {Developed an unmanned aerial vehicle (UAV) obstacle-aware positioning algorithm for simple scenarios with a collaborative student team.}
        \item {Received an honorable mention recognition for internship performance.}
        \item {Technologies used: Python, Git, NS-3}
      \end{cvitems}
    }
    {Capstone Research Intern} 
    {Feb. 2024 - Jun. 2024} 
    {
      \begin{cvitems}
      \item {Developed a custom Extended Kalman Filter (EKF) SLAM algorithm for real-time autonomous vehicle state estimation.}
      \item {Fused IMU, wheel speed, and perception sensor data to predict pose, velocities, and map track cones.}
      \item {Technologies used: C++, ROS2, Linux}
      \end{cvitems}
    }

\end{cventries}